On The Impact of Atoms of Confusion in JavaScript Code

### 2021-04-20 1_Introduction.tex
additional review of the Introduction

Source code misunderstandings can occur due to diverse reasons.
A poorly understood requirement might lead to poorly implemented code.
An intricate algorithm may require extra time to be fully comprehended.
Nevertheless, programming languages can also be at fault.
Specific syntax and semantics of a language can cause misunderstandings. The same applies to some code idioms and stylistic choices~\cite{DBLP:conf/msr/GopsteinZFC18}.

@@

JavaScript is the most widely used language for web development and the most often adopted language on GitHub~\cite{BugsJS:ICST}. At the same time, JavaScript is infamously known to be ``the worst most popular language in the world''.\footnote{\url{https://github.com/getify/You-Dont-Know-JS/blob/2nd-ed/preface.md}} It is a weakly typed language~\cite{DynamicBehaviorJS:PLDI} that provides object-oriented, functional, and imperative constructs~\cite{JS-CodeSmells:SCAM}, in addition to features such as run-time evaluation~\cite{BugsJS:ICST,ClientSideBugsJS:TSE}, and asynchronous operations. All these 
%diverse characteristics and capabilities
features combined make JavaScript source code fertile ground for errors~\cite{BugsJS:ICST,ClientSideBugsJS:TSE} and confusion~\cite{JSGoodParts:book}.

Our research aims to help practitioners identify potentially confusing snippets of code and alternative snippets that can make the code clearer.
To achieve that, we investigate {\color{red}XYZ} JavaScript idioms that
might negatively impact program understanding. These idioms correspond to a set of candidates for \emph{atoms of confusion} in
JavaScript---that is, small
pieces of code that hinder developers' understanding of the source code of a program
for which there are functionally equivalent alternatives that are easier
to understand~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}. For instance, consider
the pair of code snippets in Listing~\ref{fig:lst01} (adapted from \textsc{NervJS/taro}).
%for presentation purpose only). 
The code on the left-hand side of the figure contains two atoms of confusion discussed in previous work focusing on the C language~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}: \emph{Logic as Control Flow} and \emph{Post-increment}. On the right-hand side, we present a cleaned version of the code, that is, without atoms of confusion. In the experiments of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}, removing the atoms \emph{Logic as Control Flow} and \emph{Post-increment} improved the accuracy of program understanding tasks in  41\% and 34\%, respectively.

Recent work~\cite{DBLP:journals/ese/MedeirosLAAKRG19,DBLP:conf/sigsoft/GopsteinIYDZYC17,Langhout:2021:ACJ} has explored the impact of atoms of confusion on program understanding, and confirmed they negatively impact source code readability.
However, these previous studies focus exclusively on statically typed languages (e.g., \clang and \cpplang). To the best of our knowledge, we are the first to explore atoms of confusion in the context of a dynamically typed language (JavaScript).\castor{Review the number of atoms, X, and Y.}  JavaScript's programming culture differs from that of languages such as C and Java, e.g., because there are no types and due to the pervading use of callbacks. Thus, we may find that idioms and constructs that are atoms of confusion in those languages are not particularly difficult to understand for JavaScript programmers and vice-versa.
\castor{The following should probably be left out. I don't think we investigate atoms outside of those that were already studied in C. Or maybe say explicitly that we are studying a group of atoms that stems from the previous study?}
Furthermore, among the atom candidates we investigate in this work, {\color{red}X} are shared between JavaScript and \clang/\cpplang (e.g., pre/post-increment), while {\color{red}Y} others are specific to JavaScript, e.g., the atom Assignment as Value.

@@

To understand whether an atom of confusion introduces misunderstandings, we surveyed 140 developers from the Reddit community.\footnote{\url{https://www.reddit.com/r/javascript/comments/bw36h6/academic_research_on_confusing_code_on_javascript/}}
Their task was to predict the output of short snippets of code, with half of them containing atoms of confusion. 
\castor{Improvement of 15\% in terms of what. This is too loose.} We found an improvement of at least 15\% in the correct answers when removing the confusing code for seven atoms (out of 9 atoms). The presence of the Comma Operator atom, for instance, can increase the average time to predict the output by 65\%, while the behavior of snippets containing the Pre-Increment atom were predicted 44\% faster.  The presence or absence of atoms in open-source repositories may reveal cases where developers should be more or less careful when writing code. To identify such cases, we mined the 100 most popular JavaScript projects from GitHub and found a total of {\color{red}X} atoms in the analyzed projects. To learn more about the misunderstandings in the snippets used in the survey, we interviewed 15 experienced professional developers. Participants preferred code snippets \textit{without} an atom in 70\% of the cases, therefore corroborating with the survey findings. During the MSR and interview studies, we also explored additional atom candidates that are specific to the
JavaScript language.

>>>>

Source code misunderstandings can occur due to diverse reasons.
For instance, a poorly understood requirement might lead to poorly implemented code.
An intricate algorithm may require extra time to be fully comprehended.
Besides that, programming languages can also be at fault
and specific syntax and semantics of a language can cause misunderstandings. The same applies to some code
idioms and stylistic choices~\cite{DBLP:conf/msr/GopsteinZFC18}.

@@

This research focus on existing JavaScript idioms that a previous 
research work have proved to introduce misunderstanding in \clang.
JavaScript the most widely used language for web development and the most often adopted language on GitHub~\cite{BugsJS:ICST}. At the same time, JavaScript is infamously known to be ``the worst most popular language in the world''.\footnote{\url{https://github.com/getify/You-Dont-Know-JS/blob/2nd-ed/preface.md}} It is a weakly typed language~\cite{DynamicBehaviorJS:PLDI} that provides object-oriented, functional, and imperative constructs~\cite{JS-CodeSmells:SCAM}, in addition to features such as run-time evaluation~\cite{BugsJS:ICST,ClientSideBugsJS:TSE}, and asynchronous operations. All these 
%diverse characteristics and capabilities
features combined make JavaScript source code fertile ground for errors~\cite{BugsJS:ICST,ClientSideBugsJS:TSE} and confusion~\cite{JSGoodParts:book}.

In particular, our research aims to help practitioners identify potentially confusing snippets of code and alternative snippets that can make the code clearer.
To achieve that, we investigate JavaScript idioms that
might negatively impact program understanding. These idioms correspond to a set of candidates for \emph{atoms of confusion} in
JavaScript---that is, small
pieces of code that hinder developers' understanding of the source code of a program
for which there are functionally equivalent alternatives that are easier
to understand~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}. For instance, consider
the pair of code snippets in Listing~\ref{fig:lst01} (adapted from \textsc{NervJS/taro}).
%for presentation purpose only). 
The code on the left-hand side of the figure contains two atoms of confusion discussed in previous work focusing on the \clang
language~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}: \emph{Logic as Control Flow} and \emph{Post-increment}. On the right-hand side, we present a cleaned version of the code, that is, without atoms of confusion. In the experiments of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}, removing the atoms \emph{Logic as Control Flow} and \emph{Post-increment} improved the accuracy of program understanding tasks in  41\% and 34\%, respectively.

Recent work~\cite{DBLP:journals/ese/MedeirosLAAKRG19,DBLP:conf/sigsoft/GopsteinIYDZYC17,Langhout:2021:ACJ} has explored the impact of atoms of confusion on program understanding, and confirmed they negatively impact source code readability.
However, these previous studies focus exclusively on statically typed languages (e.g., \clang, \cpplang, and Java). However, JavaScript's programming culture differs from that of languages such as \clang and \cpplang, particularly due to the JavaScript's dynamic
capabilities and weaker type system. Thus, we may find that idioms and constructs that are atoms of confusion in those languages are not particularly difficult to understand for JavaScript programmers and vice-versa. Here we investigate a group of atom candidates
that stems from the Gopstein et al. study and detail additional JavaScript constructs
that might introduce misunderstanding---according to the opinion of JavaScript
developers.

@@

To understand whether an atom of confusion introduces misunderstandings,
we surveyed 140 JavaScript developers. In the survey, 
their task was to predict the output of short code
snippets, with half of them containing atoms of confusion. 
\castor{Improvement of 15\% in terms of what. This is too loose.}
       {\color{red}The number of correct answers for the
         cleaned version of the code snippets for seven (out of nine)
         atom candidates is at least 15\% higher, in comparison to the version
         of the code with the atoms. The presence of an atom candidate
       might also affects the time necessary for submitting a correct answer.}
       For instance, the presence of the Comma Operator atom increases
       the average time to predict the output by 65\%, though the output of snippets containing
       the Pre-Increment atom were correctly predicted 44\% faster.
       To learn more about the misunderstandings in the snippets used in the survey, we interviewed 15
       experienced professional developers. Participants preferred code snippets \textit{without} an atom in 70\% of the cases,
       therefore corroborating with the survey findings. The participants also discussed additional 
       idioms that might lead developers to incorrectly comprehend the JavaScript code.
       The occurrence of atoms in open-source repositories may reveal cases where developers
       should be more or less careful when writing code. To identify such cases, we mined popular JavaScript projects
       from GitHub and found that four atoms are highly used in JavaScript
       code: the Implicit Predicate atom, for instance, occurs 19.89 times per KLOC of
       code.
